A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-03 manuscript.Rmd
add placeholder for GitHub collaboration
explain the basics of issues #20

<!--Hands on: Introduce GitHub Issues-->
<!--Hands on: Introduce GitHub Projects-->

>>>>

### GitHub Issues

<!--Hands on: Introduce GitHub Issues-->
Effective collaboration needs effective organization.
GitHub offers a ticket system called "Issues".
Here you and your collaborators can discuss and distribute tasks.

To take a look at the issue page of your project, you may use:

``` r
usethis::browse_github_issues()
```

```{r issue-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
issue <- here::here("images", "issue.png")
if(!file.exists(issue)){
  webshot2::webshot("https://github.com/aaronpeikert/repro-tutorial/issues/20",
                  file = issue,
                  selector = "div#repo-content-pjax-container", # only select file change
                  zoom = 2)# higher resolution
}
```

```{r issue, echo=FALSE, fig.cap="A screenshot of an example issue.  ", out.width='100%'}
knitr::include_graphics(issue)
```

One advantage of using the issue system of GitHub is that it enables you to link changes you made to their tasks by including the issue number (i.e. #20) in the commit message:

``` r
# do not run this
gert::git_add(c("manuscript.Rmd", "references.bib"))
gert::git_commit("explain the basics of issues #20")
```

While it is a valuable device for working with direct collaborators, it is also great to facilitate review [@rougierSustainableComputationalScience2017].
Even if a journal does not support this, it enables post-publication review.
Readers of your manuscript can ask questions or point out how to improve it after you have published it.

### GitHub Pull Requests

<!--Hands on: Introduce GitHub PR and review-->

### GitHub Project Management

<!--Hands on: Introduce GitHub Projects-->
